---
title: "individual1ZL.Rmd"
author: "Zack Larson"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the Data
```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

## Searching for the Best Chocolates
#### 1.
The ratings are distributed unevenly. As you can see in the histogram, there are a lot more ratings greater than 2.5 than lower than 2.5. In the box plot, you can also see that the data is more relevant in the upper ratings like 3 and 3.5 than down below in the 2.5 and 2 ratings, Since the ratings vary from 1-4, the average before data should be around 2.5 but is in fact 3.184 showing that its skewed more to the higher ratings.There are not many outliers, there are a few 1 ratings, but overall that is expected with such a large collection of data.
```{r}
ratings <- choco$Rating
hist(ratings)
boxplot(ratings)
averageRating <- mean(ratings)
averageRating
```

#### 2.
The number of ratings depend on the location of the company because some places might not have as many reviewers in their area as opposed to others.For example, there are a lot more ratings of Australian companies than Czech Republic companies because the population of Australia is that much bigger.
```{r}
library(ggplot2)
ggplot(aes(x = Rating,fill=Location),data=choco) + geom_bar()
```

#### 3.
As shown in the scatter plot, the columns showing the cocoa percentage and the rating of the chocolate bar has no relation at all. Also as shown in the cor() function, the 2 columns show no strength of correlation at all too.A scatter plot is not the best choice here because there are so many ratings and cocoa percentages that are similar or equal in value so overlapping in values shown in the scatter plot can be overlooked. 
```{r}
plot(choco$Rating,choco$Cocoa_Percent)
cor(choco$Rating,choco$Cocoa_Percent)
```
## Collaboration Workflow - Zack Larson
#### 4.
There are certain trends among the correlation between bean origin and overall rating. In general, there are not a lot of bean origins that have a wide variety of ratings for them. It is usually determined from the consensus that the reviewers are on the same page when it comes to the ratings. For example, Peru has way higher ratings and number of 4/4 ratings than Berma where they have a high average rating (in the top 20) but don't have as many 4/4 ratings as Peru who looks to have the most.This is confirmed by the numerical analysis that shows that Peru is the bean origin for several chocolate bars in the top 20 of average ratings.
```{r}
 best20 = choco[order(ave(choco$Rating), decreasing= TRUE),]
best20 = best20[1:20,]
ggplot(best20, aes(x=Bean_Origin, y=Rating)) + geom_count()
best20
```

#### 5.
For my analysis, I looked at the potential correlation between reviewer's characteristics of the chocolate bar with their rating of the bar. This will help dictate whether or not certain chocolate bar characteristics lead to a higher taste rating. I created one column for all characteristics and then found the average rating for each unique characteristic. After that, I found all of the characteristics who had the highest rating of 4 as the characteristic's average rating. With the graph, I displayed the top characteristics that appeared in a 4 rating bar the most times.As you can see, even though cocoa is not the best on average, it is still one of the most popular characteristics among bars with a 4 rating.
```{r}
library(tidyverse)
characteristicsRatings = choco[,c(9,10,11,12,13)]
df2 <- data.frame(Characteristics1 = c(characteristicsRatings[,"Characteristics2"], characteristicsRatings[,"Characteristics3"],characteristicsRatings[,"Characteristics4"]),characteristicsRatings[,"Rating"])##Get all characteristics into one column
groupBest <- aggregate(characteristicsRatings....Rating..~Characteristics1, df2, FUN=mean)##Get average rating of each characteristic
groupBest <- groupBest %>% slice_max(characteristicsRatings....Rating..)##Show ones with highest average rating
groupBest##Shows list of all characteristics with an average rating of 4(max)

df2 <- df2 %>% filter(characteristicsRatings....Rating.. == 4,Characteristics1!="<NA>")##Get rid of N/A data and filter for top ratings
df2 <- df2 %>% group_by(Characteristics1) %>% filter(n() > 3)##Filter for most used characteristics in the high ratings
ggplot(df2, aes(x=Characteristics1)) + geom_bar()##graph
```
