---
title: "Team.Rmd"
author: "Zack Larson, Julia Lundstrum, and Nikole Slinger"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Reading the Data
```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 
```

## Searching for the Best Chocolates
#### 1.
The ratings are distributed unevenly. As you can see in the histogram, there are a lot more ratings greater than 2.5 than lower than 2.5, making it unsymmetrical and left skewed. An interesting feature is the fact that there appears to be no chocolate with a rating between 3.0 and 3.25 when we would expect there to be many. There are also a few outliers visible below 2.0.

In the box plot, you can also see that the data is more relevant in the upper ratings like 3 and 3.5 than down below in the 2.5 and 2 ratings, Since the ratings vary from 1.0 to 4.0, the average for the data should be around 2.5 but is in fact 3.184 showing that it's skewed more to the higher ratings. There are not many outliers, there are a few 1.0 ratings, but overall that is expected with such a large collection of data.
```{r}
ratings <- choco$Rating
hist(ratings, col = "navy")
boxplot(ratings, main = 'Chocolate Rating', ylab = 'Rating', col = "orange")
averageRating <- mean(ratings)
averageRating
```

#### 2.
The location of the company appears to have little effect on the rating of the chocolate because there are multiple companies with the same location but with different chocolate ratings. For example, companies that are located in U.S.A. seem to have ratings that range between about 2.0 and 4.0. However, one way that location may have a small effect on chocolate rating is that there may be more reviewers in one country than in another. For example, there are a lot more ratings of Australian companies than Czech Republic companies because the population of Australia is that much bigger.
```{r, fig.width=5, fig.height=8}
library(ggplot2)
ggplot(aes(x = Rating,fill=Location),data=choco) + geom_histogram(bins = 13) + theme(legend.position = "bottom")
```

#### 3.
As shown in the scatter plot, the columns showing the cocoa percentage and the rating of the chocolate bar seem to have no linear relationship at all. Also as shown in the cor() function, the correlation coefficient is r = -0.151, meaning that the 2 variables show extremely little strength of correlation (if anything, there is a very small negative correlation). One note to make is that a scatter plot is not the best choice of graph here because there are so many ratings and cocoa percentages that are similar or equal in value so overlapping in values shown in the scatter plot can be overlooked. 
```{r}
plot(choco$Rating,choco$Cocoa_Percent, main = 'Chocolate Rating vs. Cocoa Percent', xlab = 'Rating', ylab = 'Cocoa Percentage')
cor(choco$Rating,choco$Cocoa_Percent)
newdf <- choco
newdf$Rating=factor(newdf$Rating)
ggplot(newdf, aes(Cocoa_Percent, fill = Rating)) + geom_histogram(bins = 20) + ggtitle("Ratings of Cocoa Percents") + ylab("Number of Ratings") + xlab("Cocoa Percent")
```
## Collaboration Workflow - Zack Larson
#### 4.
There are certain trends among the correlation between bean origin and overall rating. In general, there are not a lot of bean origins that have a wide variety of ratings for them. It is usually determined from the consensus that the reviewers are on the same page when it comes to the ratings. For example, Peru has way higher ratings and number of 4/4 ratings than Berma where they have a high average rating (in the top 20) but don't have as many 4/4 ratings as Peru who looks to have the most.This is confirmed by the numerical analysis that shows that Peru is the bean origin for several chocolate bars in the top 20 of average ratings.
```{r}
 best20 = choco[order(ave(choco$Rating), decreasing= TRUE),]
best20 = best20[1:20,]
ggplot(best20, aes(x=Bean_Origin, y=Rating)) + geom_count()
best20
```

#### 5.
For my analysis, I looked at the potential correlation between reviewer's characteristics of the chocolate bar with their rating of the bar. This will help dictate whether or not certain chocolate bar characteristics lead to a higher taste rating. I created one column for all characteristics and then found the average rating for each unique characteristic. After that, I found all of the characteristics who had the highest rating of 4 as the characteristic's average rating. With the graph, I displayed the top characteristics that appeared in a 4 rating bar the most times.As you can see, even though cocoa is not the best on average, it is still one of the most popular characteristics among bars with a 4 rating.
```{r}
library(tidyverse)
characteristicsRatings = choco[,c(9,10,11,12,13)]
df2 <- data.frame(Characteristics1 = c(characteristicsRatings[,"Characteristics2"], characteristicsRatings[,"Characteristics3"],characteristicsRatings[,"Characteristics4"]),characteristicsRatings[,"Rating"])##Get all characteristics into one column
groupBest <- aggregate(characteristicsRatings....Rating..~Characteristics1, df2, FUN=mean)##Get average rating of each characteristic
groupBest <- groupBest %>% slice_max(characteristicsRatings....Rating..)##Show ones with highest average rating
groupBest##Shows list of all characteristics with an average rating of 4(max)

df2 <- df2 %>% filter(characteristicsRatings....Rating.. == 4,Characteristics1!="<NA>")##Get rid of N/A data and filter for top ratings
df2 <- df2 %>% group_by(Characteristics1) %>% filter(n() > 3)##Filter for most used characteristics in the high ratings
ggplot(df2, aes(x=Characteristics1)) + geom_bar()##graph
```

## Collaboration Workflow - Nikole Slinger
#### 4.

```{r}
# creating boxplots of bean origins and their ratings
boxplot(choco$Rating ~ choco$Bean_Origin, main = "Chocolate Ratings of Different Bean Origins",
        xlab = "Country", ylab = "Rating", las = 2)
```

From looking at the multiple boxplots, we can see that the most common median value is between 3.0 and 3.25. The country of Tobago appears to have the highest chocolate rating interquartile range, while Uganda seems to have the lowest chocolate rating interquartile range.

```{r}
# only using top 50
ratings = choco[order(ave(choco$Rating), decreasing= TRUE), ]
ratings = ratings[1:50, ]
ggplot(ratings, aes(x = Bean_Origin, y = Rating)) + geom_count() +
  theme(axis.text.x = element_text(angle = 90))
```

From this plot, it's important to note that we are only looking at the top 100 ratings for bean origins. Based on this, we can see that the majority of the countries on this graph are from South America and virtually all are located near the equator. From this, we can see that better chocolate ratings are correlated with countries with hot and rainy climates, specifically Peru, which has noticeably higher chocolate ratings compared to the other countries.

#### 5.

```{r}
library(tidyverse)

# looking at companies with highest chocolate ratings
companydata <- choco[,c(2, 13)]
codata <- data.frame(company = c(companydata[,"Company"]), companydata[,"Rating"])
topcompanies <- aggregate(companydata....Rating..~company, codata, FUN=mean)
# finding companies with chocolate ratings above 3.75
topcompanies <- topcompanies %>% slice_max(companydata....Rating.. > 3.75)
topcompanies
```

For my analysis I looked for the companies with the top average chocolate rating. I found that the  companies returned above had the highest chocolate ratings (those above 3.75). The location of these companies include U.S.A, Switzerland, Australia, Scotland, and France while the bean origins include Bolivia, Venezuela, Madagascar, and Tobago (among others). Even though the company locations are not located where the beans come from, we know from previous anaylses that bean origin is what has a larger effect on chocolate rating.

## Collaboration Workflow - Julia Lundstrum
#### 4.
```{r}
new2 <- choco[, c('Bean_Origin','Rating')]
aggregate(new2[, 2], list(new2$Bean_Origin), mean)
ggplot(newdf, aes(Bean_Origin, fill = Rating)) + geom_bar() + ggtitle("Ratings of Bean Origins") + ylab("Number of Ratings") + xlab("Bean Origin") + theme(axis.text.x = element_text(angle = 90))
boxplot(choco$Rating ~ choco$Bean_Origin, col=c("green","yellow","navy","orange"), main = "Ratings by Bean Origin", xlab = "Bean Origin", ylab = "Rating", las = 2)
```

There does not appear to be a significant relationship between bean origin and the rating of the chocolate. The mean rating for the different bean origins are about the same. There are a few that are a bit higher, but the sample size is not large enough to determine if that was just by chance.

#### 5.
```{r}
new3 <- choco[, c('Date','Rating')]
corr2 <- round(cor(new3),2)
corr2
summary(new3)
newdf2 <- choco
newdf2$Rating=factor(newdf2$Rating)
newdf2$Date=factor(newdf2$Date)
ggplot(newdf2, aes(Date, fill = Rating)) + geom_bar() + ggtitle("Ratings by Year") + ylab("Number of Ratings") + xlab("Year")
boxplot(choco$Rating ~ choco$Date, col=c("skyblue","royalblue","ivory","navy","springgreen"), main = "Ratings by Year", xlab = "Year", ylab = "Rating", las = 2)
```

I decided to analyze the relationship between ratings and what year they were rated. There is not a correlation between the year rated and rating received. I used a stacked bar graph and box plots to analyze the data. 